Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis

### 2016-04-08 manuscript/manuscript_pve.Rmd
deleted unused files
manuscript edits from BM

new CUE figures

added new phyt cites

---
title: Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_newphyt.docx
  pdf_document: default
  html_document:
    number_sections: yes

csl: new-phytologist.csl
bibliography: references2.bib
---

@@

Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration. As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate among different tissues and organs. At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and will correlate to plant growth. At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools. This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity. Consequently, plant growth cannot always be simply determined by *A*~n~, making it complex to understand and challenging to model [@fourcaud2008plant]. Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.

@@

# Acknowledgements
We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest. This research was funded by a PhD Scholarship drom the Hawkesbury Institute for the Environment (Western Sydney University).

>>>>

---
title: Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_newphyt.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references2.bib
---

@@

Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration. As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth should principally depend on the allocation of photosynthate from source leaves among different tissues and organs. At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and will correlate to plant growth. At shorter temporal scales, however, growth can instead be mediated by tissue C storage pools. This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity. Consequently, plant growth cannot always be simply determined by *A*~n~, making it complex to understand and challenging to model [@fourcaud2008plant]. Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.

@@

# Acknowledgements
We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest. This research was funded by a PhD Scholarship from the Hawkesbury Institute for the Environment (Western Sydney University).
